```{r}
date = as.Date("2020-01-19")

game_id= 638
```



```{r}
library(dplyr)
library(readxl)
winner <- read_excel("WINNER_with_date.xlsx")
winner$ID = c(1:nrow(winner))
winner$GDate = as.Date(winner$GDate)
winner$code = paste(winner$Away,"vs",winner$Home,sep = "-")
winner= winner %>% na.omit()
winner$HOME_WIN = as.factor(winner$HOME_WIN)
winner$ALastGameAgo = as.numeric(winner$ALastGameAgo)
winner$HLastGameAgo = as.numeric(winner$HLastGameAgo)
winner=winner %>% mutate_if(is.character, as.factor)

        test = winner %>% filter(ID==game_id)
        train = winner %>% filter(GDate < date)
```

```{r}
library(readxl)
total <- read_excel("TOTAL_with_date.xlsx")
total$ID = c(1:nrow(total))
total$GDate = as.Date(total$GDate)
total$code = paste(total$Away,"vs",total$Home,sep = "-")
total= total %>% na.omit()
total$ALastGameAgo = as.numeric(total$ALastGameAgo)
total$HLastGameAgo = as.numeric(total$HLastGameAgo)
total=total %>% mutate_if(is.character, as.factor)


test = total %>% filter(ID==game_id)
train = total %>% filter(GDate < date)

```

```{r}

library(readxl)
fora <- read_excel("FORA_with_date.xlsx")
fora$ID = c(1:nrow(fora))
fora$GDate = as.Date(fora$GDate)
fora$code = paste(fora$Away,"vs",fora$Home,sep = "-")
fora= fora %>% na.omit()
fora$ALastGameAgo = as.numeric(fora$ALastGameAgo)
fora$HLastGameAgo = as.numeric(fora$HLastGameAgo)
fora=fora %>% mutate_if(is.character, as.factor)

test = fora %>% filter(ID==game_id)
train = fora %>% filter(GDate < date)
```





```{r}
win=winner[1:2,]
NEWTEST = win[1:round(0.7*nrow(win)),]
NEWTEST2 = win[ceiling(0.7*nrow(win)):nrow(win),]



```



```{r}
        test = winner %>% filter(ID==game_id)
        train = winner %>% filter(GDate < date)
        test = test %>% select(-GDate,-code,ID)
        train = train %>% select(-GDate,-code,ID)
        train <- as.data.frame(unclass(train)) 
        test = as.data.frame(unclass(test))
        #####CODE#####
        debug_contr_error <- function (train, subset_vec = NULL) {
          if (!is.null(subset_vec)) {
            ## step 0
            if (mode(subset_vec) == "logical") {
              if (length(subset_vec) != nrow(train)) {
                stop("'logical' `subset_vec` provided but length does not match `nrow(train)`")
              }
              subset_log_vec <- subset_vec
            } else if (mode(subset_vec) == "numeric") {
              ## check range
              ran <- range(subset_vec)
              if (ran[1] < 1 || ran[2] > nrow(train)) {
                stop("'numeric' `subset_vec` provided but values are out of bound")
              } else {
                subset_log_vec <- logical(nrow(train))
                subset_log_vec[as.integer(subset_vec)] <- TRUE
              }
            } else {
              stop("`subset_vec` must be either 'logical' or 'numeric'")
            }
            train <- base::subset(train, subset = subset_log_vec)
          } else {
            ## step 1
            train <- stats::na.omit(train)
          }
          if (nrow(train) == 0L) warning("no complete cases")
          ## step 2
          var_mode <- sapply(train, mode)
          if (any(var_mode %in% c("complex", "raw"))) stop("complex or raw not allowed!")
          var_class <- sapply(train, class)
          if (any(var_mode[var_class == "AsIs"] %in% c("logical", "character"))) {
            stop("matrix variables with 'AsIs' class must be 'numeric'")
          }
          ind1 <- which(var_mode %in% c("logical", "character"))
          train[ind1] <- lapply(train[ind1], as.factor)
          ## step 3
          fctr <- which(sapply(train, is.factor))
          if (length(fctr) == 0L) warning("no factor variables to summary")
          ind2 <- if (length(ind1) > 0L) fctr[-ind1] else fctr
          train[ind2] <- lapply(train[ind2], base::droplevels.factor)
          ## step 4
          lev <- lapply(train[fctr], base::levels.default)
          nl <- lengths(lev)
          ## return
          b = list(nlevels = nl, levels = lev)
          assign("be", b, envir = .GlobalEnv)
        }
        
        debug_contr_error(train)
        be$nlevels
        factors <- which(sapply(train, is.factor))
        
        BAD = c(as.numeric(be$nlevels[1]) != 30, as.numeric(be$nlevels[2]) != 30, as.numeric(be$nlevels[3]) != 2, as.numeric(be$nlevels[4]) != 2, as.numeric(be$nlevels[5]) != 2, as.numeric(be$nlevels[6]) != 2, as.numeric(be$nlevels[7]) != 3, as.numeric(be$nlevels[8]) != 2, as.numeric(be$nlevels[9]) != 2, as.numeric(be$nlevels[10]) != 1)
        
        WORSE = factors[BAD]
        #####CODE#####
        formula <- as.formula(paste(colnames(train)[222],'~', colnames(train)[-WORSE]))
        
        log.model = glm(formula, data = train, family = binomial(link = 'logit'))
        

        Log.train = predict(log.model, newdata = train, type = "response")
        Log.test = predict(log.model, newdata = test, type = "response")
        
        Log.pred.train0.5 = ifelse(Log.train > 0.5,1,0)
        Log.pred.test0.5 = ifelse(Log.test > 0.5,1,0)
        
        
        test$Home=as.character(test$Home)
        test$Away=as.character(test$Away)
        
            if (as.numeric(Log.test) > 0.5){
            
            result = test[1,"Home"]
            coeff = test[1,4]
            
            } else {
            result = test[1,"Away"]
            coeff = test[1,2]
            }    
        
        
        
        test$value_home = Log.test * 100 * (test$HODD - 1) - (1-Log.test) * 100
        test$value_away = (1-Log.test) * 100 * (test$AODD - 1) - Log.test * 100
        
        test$team = case_when(
          (test$value_home >= test$value_away) & (test$value_home > 0) ~ test$Home,
          (test$value_away >= test$value_home) & (test$value_away > 0) ~ test$Away,
          TRUE ~ "0")
        
        test$coeff = dplyr::case_when(
          test$team == test$Home ~ test$HODD,
          test$team == test$Away ~ test$AODD,
          TRUE ~ 0)
        
        test$prob = dplyr::case_when(
          test$team == test$Home ~ Log.test,
          test$team == test$Away ~ 1 - Log.test,
          TRUE ~ 0)
        
        if (test$team != as.factor(0)){
          str1 = paste0("The coefficients for this match are: ", round(test$HODD, digits = 3)," for ", test$Home, " and ", round(test$AODD, digits = 3), " for ", test$Away,"<br/> ", "We recommend to put a bet on ", test$team, " with a coefficient ", round(test$coeff, digits = 3), "<br/> ", "According to out prediction, ", test$team, "'s probability to win is ", round(test$prob, digits = 3),"<br/> " ,"Expected profit from this bet is ", round(max(test$value_home, test$value_away), digits = 3),".")
        } else {
          str1 = paste0("The coefficients for this match are: ", round(test$HODD, digits = 3)," for ", test$Home, " and ", round(test$AODD, digits = 3), " for ", test$Away,". There is no optimal prediction for this match: the coefficients are not profitable.")
        }
         
  
        #str1 = paste("We recommend you to bet on", paste("<b>",result,"</b>"), "with coefficient",paste("<b>",coeff,"</b>"))
        
        if (test$HOME_WIN == 1){
          
          winner = test[1, "Home"]
          
        } else {
          winner = test[1, "Away"]
        }
        
        if (((test$HOME_WIN == 1) & (test$team == test$Home)) | ((test$HOME_WIN == 0) & (test$team == test$Away))){
          
          proper = "correct"
          
        } else {
          proper = "incorrect"
        }
        
        library(stringr)
        if (str_detect(str1, "optimal")){
          str2 = paste("The true winner of this match is","<b>" ,winner,"</b>")
        } else {
          str2 = paste("The true winner of this match is","<b>" ,winner,"</b>", ", the prediction is", proper)
        }        
        
        HTML(paste(str1, str2, sep = '<br/>'))
```



```{r}
            test = winner %>% filter(ID==game_id)
            train = winner %>% filter(GDate < as.Date(date))
            test = test %>% select(-GDate,-code,-ID)
            train = train %>% select(-GDate,-code,-ID)
            train <- as.data.frame(unclass(train)) 
            test = as.data.frame(unclass(test))
            
            
            set.seed(1)
            model.rf=randomForest::randomForest(HOME_WIN~.,data=train, mtry=5, ntree = 1000)
            
            
            predTrain.rf =as.numeric(predict(model.rf, train)) - 1
            predTest.rf = predict(model.rf, test)
            predTest.rf = as.numeric(predTest.rf) - 1
            
            predTest.rf = predict(model.rf, test,"prob")[,2]
            
            
            
            if (predTest.rf > 0.5){
                
                result = test[1,"Home"]
                coeff = test[1,4]
                
            } else {
                result = test[1,"Away"]
                coeff = test[1,2]
            }    
            
            test$Home = as.character(test$Home)
            test$Away = as.character(test$Away)
            
            test$value_home = predTest.rf * 100 * (test$HODD - 1) - (1-predTest.rf) * 100
            test$value_away = (1-predTest.rf) * 100 * (test$AODD - 1) - predTest.rf * 100
            
            test$team = case_when(
              (test$value_home >= test$value_away) & (test$value_home > 0) ~ test$Home,
              (test$value_away >= test$value_home) & (test$value_away > 0) ~ test$Away,
              TRUE ~ "0")
            
            test$coeff = dplyr::case_when(
              test$team == test$Home ~ test$HODD,
              test$team == test$Away ~ test$AODD,
              TRUE ~ 0)
            
            test$prob = dplyr::case_when(
              test$team == test$Home ~ Log.test,
              test$team == test$Away ~ 1 - Log.test,
              TRUE ~ 0)
            
            if (test$team != as.factor(0)){
              str1 = paste0("The coefficients for this match are: ", round(test$HODD, digits = 3)," for ", test$Home, " and ", round(test$AODD, digits = 3), " for ", test$Away,"<br/> ", "We recommend to put a bet on ", test$team, " with a coefficient ", round(test$coeff, digits = 3), "<br/> ", "According to out prediction, ", test$team, "'s probability to win is ", round(test$prob, digits = 3),"<br/> " ,"Expected profit from this bet is ", round(max(test$value_home, test$value_away), digits = 3),".")
            } else {
              str1 = paste0("The coefficients for this match are: ", round(test$HODD, digits = 3)," for ", test$Home, " and ", round(test$AODD, digits = 3), " for ", test$Away,". There is no optimal prediction for this match: the coefficients are not profitable.")
            }
            
            
            #str1 = paste("We recommend you to bet on", paste("<b>",result,"</b>"), "with coefficient",paste("<b>",coeff,"</b>"))
            
            if (test$HOME_WIN == 1){
              
              winner = test[1, "Home"]
              
            } else {
              winner = test[1, "Away"]
            }
            
            if (((test$HOME_WIN == 1) & (as.factor(test$team) == test$Home)) | ((test$HOME_WIN == 0) & (as.factor(test$team) == test$Away))){
              
              proper = '<font color="	#008000">correct</font>'
              
            } else {
              proper = '<font color="	#ff0000">incorrect</font>'
            }
            
            library(stringr)
            if (str_detect(str1, "optimal")){
              str2 = paste("The true winner of this match is","<b>" ,winner,"</b>")
            } else {
              str2 = paste("The true winner of this match is","<b>" ,winner,"</b>", ", the prediction is", proper)
            }        
            
            HTML(paste(str1, str2, sep = '<br/>'))
```




```{r}
            test = winner %>% filter(ID==game_id)
            train = winner %>% filter(GDate < as.Date(date))
            test = test %>% select(-GDate,-code,-ID)
            train = train %>% select(-GDate,-code,-ID)
            train <- as.data.frame(unclass(train)) 
            test = as.data.frame(unclass(test))
            #####CODE#####
            debug_contr_error <- function (train, subset_vec = NULL) {
              if (!is.null(subset_vec)) {
                ## step 0
                if (mode(subset_vec) == "logical") {
                  if (length(subset_vec) != nrow(train)) {
                    stop("'logical' `subset_vec` provided but length does not match `nrow(train)`")
                  }
                  subset_log_vec <- subset_vec
                } else if (mode(subset_vec) == "numeric") {
                  ## check range
                  ran <- range(subset_vec)
                  if (ran[1] < 1 || ran[2] > nrow(train)) {
                    stop("'numeric' `subset_vec` provided but values are out of bound")
                  } else {
                    subset_log_vec <- logical(nrow(train))
                    subset_log_vec[as.integer(subset_vec)] <- TRUE
                  }
                } else {
                  stop("`subset_vec` must be either 'logical' or 'numeric'")
                }
                train <- base::subset(train, subset = subset_log_vec)
              } else {
                ## step 1
                train <- stats::na.omit(train)
              }
              if (nrow(train) == 0L) warning("no complete cases")
              ## step 2
              var_mode <- sapply(train, mode)
              if (any(var_mode %in% c("complex", "raw"))) stop("complex or raw not allowed!")
              var_class <- sapply(train, class)
              if (any(var_mode[var_class == "AsIs"] %in% c("logical", "character"))) {
                stop("matrix variables with 'AsIs' class must be 'numeric'")
              }
              ind1 <- which(var_mode %in% c("logical", "character"))
              train[ind1] <- lapply(train[ind1], as.factor)
              ## step 3
              fctr <- which(sapply(train, is.factor))
              if (length(fctr) == 0L) warning("no factor variables to summary")
              ind2 <- if (length(ind1) > 0L) fctr[-ind1] else fctr
              train[ind2] <- lapply(train[ind2], base::droplevels.factor)
              ## step 4
              lev <- lapply(train[fctr], base::levels.default)
              nl <- lengths(lev)
              ## return
              b = list(nlevels = nl, levels = lev)
              assign("be", b, envir = .GlobalEnv)
            }
            
            debug_contr_error(train)
            be$nlevels
            factors <- which(sapply(train, is.factor))
            BAD = c(as.numeric(be$nlevels[1]) != 30, as.numeric(be$nlevels[2]) != 30, as.numeric(be$nlevels[3]) != 2, as.numeric(be$nlevels[4]) != 2, as.numeric(be$nlevels[5]) != 2, as.numeric(be$nlevels[6]) != 2, as.numeric(be$nlevels[7]) != 3, as.numeric(be$nlevels[8]) != 2, as.numeric(be$nlevels[9]) != 2, as.numeric(be$nlevels[10]) != 1)
            WORSE = factors[BAD]
            #####CODE#####
            formula <- as.formula(paste(colnames(train)[222],'~', colnames(train)[-WORSE]))
            log.model = glm(formula, data = train, family = binomial(link = 'logit'))
            
            Log.train = predict(log.model, newdata = train, type = "response")
            Log.test = predict(log.model, newdata = test, type = "response")
            
            Log.pred.train0.5 = ifelse(Log.train > 0.5,1,0)
            Log.pred.test0.5 = ifelse(Log.test > 0.5,1,0)

            
            test = winner %>% filter(ID==game_id1())
            train = winner %>% filter(GDate < as.Date(input$date))
            test = test %>% select(-GDate,-code,-ID)
            train = train %>% select(-GDate,-code,-ID)
            train <- as.data.frame(unclass(train)) 
            test = as.data.frame(unclass(test))
            
            set.seed(1)
            model.rf=randomForest::randomForest(HOME_WIN~.,data=train, mtry=5, ntree = 1000)
            
            
            predTrain.rf =as.numeric(predict(model.rf, train)) - 1
            predTest.rf = predict(model.rf, test)
            predTest.rf = as.numeric(predTest.rf) - 1

            test = winner %>% filter(ID==game_id)
            train = winner %>% filter(GDate < as.Date(date))
            test = test %>% select(-GDate,-code,-ID)
            train = train %>% select(-GDate,-code,-ID)
            
            train$HOME_WIN = as.numeric(train$HOME_WIN) - 1
            test$HOME_WIN = as.numeric(test$HOME_WIN) - 1
            
            train1 = fastDummies::dummy_cols(train,remove_selected_columns = T,remove_first_dummy = TRUE)
            test1 = fastDummies::dummy_cols( test,remove_selected_columns = T,remove_first_dummy = TRUE)
            
            nn=neuralnet(HOME_WIN~.,data=(train1 %>% na.omit()) , hidden=3,act.fct = "logistic",
                         linear.output = FALSE)
            
            
            predTrain.nn = predict(nn,train1 %>% na.omit())
            predTest.nn = predict(nn, test1 %>% na.omit())
            
            Ann.pred.train0.5 = ifelse(predTrain.nn > 0.5,1,0)
            Ann.pred.test0.5 = ifelse(predTest.nn > 0.5,1,0)
            
            
            
            test = winner %>% filter(ID==game_id)
            train = winner %>% filter(GDate < as.Date(date))
            test = test %>% select(-GDate,-code,-ID)
            train = train %>% select(-GDate,-code,-ID)
            train <- as.data.frame(unclass(train)) 
            test = as.data.frame(unclass(test))
            
            model.boost=gbm((as.numeric(HOME_WIN)-1)~., data=train, distribution="bernoulli", n.trees=2000, interaction.depth=5)
            
            predTrainProb.boost = predict(model.boost, train, n.trees = 2000, type = "response")
            predTestProb.boost = predict(model.boost, test, n.trees = 2000, type = "response")
            
            Train.pred0.5.boost <- ifelse(predTrainProb.boost> 0.5,1,0)
            Test.pred0.5.boost <- ifelse(predTestProb.boost> 0.5,1,0)
            
            
            dataStack =  data.frame(reg = Log.pred.train0.5, 
                                    rf = predTrain.rf, 
                                    ann = Ann.pred.train0.5,
                                    gbm = Train.pred0.5.boost,
                                    HOME_WIN = as.numeric(train$HOME_WIN)-1)
            
            
            model.stack = caret::train(HOME_WIN~., data=(dataStack %>% na.omit() ), method = "glm")
            
            predictionsTest = data.frame(reg = Log.pred.test0.5, rf = predTest.rf,ann = Ann.pred.test0.5, gbm = Test.pred0.5.boost, HOME_WIN = as.numeric(test$HOME_WIN)-1)
            
            
            predTest.stack = predict(model.stack, newdata = predictionsTest,"prob")
            predTrain.stack = predict(model.stack, newdata = dataStack,type = "prob")
```



















```{r}
library
library(readxl)
winner <- read_excel("D:/R/KURSACH/RABOTAEM/NBA/WINNER_with_date.xlsx")
winner$ID = c(1:nrow(winner))
winner$GDate = as.Date(winner$GDate)
winner$code = paste(winner$Away,"vs",winner$Home,sep = "-")
winner= winner %>% na.omit()
winner$HOME_WIN = as.factor(winner$HOME_WIN)
winner$ALastGameAgo = as.numeric(winner$ALastGameAgo)
winner$HLastGameAgo = as.numeric(winner$HLastGameAgo)
winner=winner %>% mutate_if(is.character, as.factor)
winner = winner %>% select(-GDate)
```

```{r}
l = 100

train = winner[1:(nrow(winner)-l),1:length(winner)]
test = winner[(nrow(winner)-l+1):nrow(winner),1:length(winner)]
rm(l)
```

```{r}
train = train %>% select(-ID,-code)
test = test %>% select(-ID,-code)


train1=train
test1=test
        
        train1$HOME_WIN = as.numeric(train1$HOME_WIN) - 1
        test1$HOME_WIN = as.numeric(test1$HOME_WIN) - 1
        
        
        
        train1 = fastDummies::dummy_cols(train1,remove_selected_columns = T,remove_first_dummy = TRUE)
        test1 = fastDummies::dummy_cols(test1,remove_selected_columns = T,remove_first_dummy = TRUE)
        nn=neuralnet(HOME_WIN~.,data=(train1 %>% na.omit()) , hidden=3,act.fct = "logistic",
                     linear.output = FALSE)
        predTrain.nn = predict(nn,train1 %>% na.omit(),type = "response")
        predTest.nn = predict(nn, test1 %>% na.omit(),type = "response")
        
        Ann.pred.train0.5 = ifelse(predTrain.nn > 0.5,1,0)
        Ann.pred.test0.5 = ifelse(predTest.nn > 0.5,1,0)

        
        
        Ann.pred.train0.5 = as.vector(Ann.pred.train0.5)
        Ann.pred.test0.5 = as.vector(Ann.pred.test0.5)
        
        test$Home=as.character(test$Home)
        test$Away=as.character(test$Away)
        
        accuracyTrain.ann = (table(Ann.pred.train0.5,train$HOME_WIN)[2,2] + table(Ann.pred.train0.5,train$HOME_WIN)[1,1])/length(Ann.pred.train0.5)
        
        accuracyTest.ann = (table(Ann.pred.test0.5,test$HOME_WIN)[2,2] + table(Ann.pred.test0.5,test$HOME_WIN)[1,1])/length(Ann.pred.test0.5)
        
       
        
        Ann.profit = case_when(
            (Ann.pred.test0.5 == test$HOME_WIN) & (Ann.pred.test0.5 == 1) ~ 100*test$HODD - 100,
            (Ann.pred.test0.5 == test$HOME_WIN) &(Ann.pred.test0.5 == 0)  ~ 100*test$AODD - 100,
            Ann.pred.test0.5 != test$HOME_WIN ~ -100
        )
        profit = sum(Ann.profit)
        
        ann = c("ANN",Ann.pred.train0.5,Ann.pred.test0.5,profit)
```




        library(fastDummies)
        
        train$HOME_WIN = as.numeric(train$HOME_WIN) - 1
        test$HOME_WIN = as.numeric(test$HOME_WIN) - 1
        
        
        
        train1 = fastDummies::dummy_cols(train,remove_selected_columns = T,remove_first_dummy = TRUE)
        test1 = fastDummies::dummy_cols(test,remove_selected_columns = T,remove_first_dummy = TRUE)
        nn=neuralnet(HOME_WIN~.,data=(train1 %>% na.omit()) , hidden=3,act.fct = "logistic",
                     linear.output = FALSE)
        predTrain.nn = predict(nn,train1 %>% na.omit())
        predTest.nn = predict(nn, test1 %>% na.omit())
        
        Ann.pred.train0.5 = ifelse(predTrain.nn > 0.5,1,0)
        Ann.pred.test0.5 = ifelse(predTest.nn > 0.5,1,0)
        
        test$Home=as.character(test$Home)
        test$Away=as.character(test$Away)
        
        
        accuracyTrain.ann = confusionMatrix(Ann.pred.train0.5, train$HOME_WIN, positive = "1")$overall["Accuracy"]
        accuracyTest.ann = confusionMatrix(Ann.pred.test0.5, test$HOME_WIN, positive = "1")$overall["Accuracy"]
        
        Ann.profit = case_when(
            (Ann.pred.test0.5 == test$HOME_WIN) & (Ann.pred.test0.5 == 1) ~ 100*test$HODD - 100,
            (Ann.pred.test0.5 == test$HOME_WIN) &(Ann.pred.test0.5 == 0)  ~ 100*test$AODD - 100,
            Ann.pred.test0.5 != test$HOME_WIN ~ -100
        )
        profit = sum(Ann.profit)
        
        ann = c("ANN",Ann.pred.train0.5,Ann.pred.test0.5,profit)
